Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-06 Documents/Paper/ms.tex
Improving caption on sinewave data

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewave_data.pdf}
\caption{The simulated data for the sinusoidal example. The solid line shows
the true signal and the points are the measurements, simulated based on a
noise standard deviation of $\sigma = 0.5$.
\label{fig:sinewave_data}}
\end{center}
\end{figure}

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewave_data.pdf}
\caption{The simulated data for the sinusoidal example. The solid line shows
the true signal which consists of a large slow oscillation and a much smaller
amplitude fast oscillation. The points are the measurements, simulated with a
noise standard deviation of $\sigma = 0.5$.
\label{fig:sinewave_data}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{trace_logl.pdf}
\caption{A ``trace plot'' of the log likelihood in the sinusoidal model, for an
MCMC chain designed to sample the posterior distribution. The two phases
have log-likelihoods around -730 and -745 respectively, however transitions
between the two phases are quite uncommon.
\label{fig:trace_logl}}
\end{center}
\end{figure}
